Target Markdown

### 2023-08-28 _targets.Rmd
added description of the code

@@

     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(name = db_path, 
                command = transcribe_database(path = here::here("data",
                                                                "raw",
                                                                "czech_sci_db.sqlite"),
                                              authors_arrow, 
                                              cep_investigators_arrow,   
                                              cep_details_arrow, 
                                              riv_details_arrow, 
                                              riv_authors_arrow,
                                              text_arrow),
                format = "file"
                )

@@

# Matching and data preparation

```{r, engine="targets", matching_preparation}
list(

     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
      tar_target(sup_control, read.csv(sup_path)),

      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded)),

       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
      tar_target(sup_control_second, read.csv(sup_path_second)),
      tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),

      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
     tar_target(random_pubs,
           get_random_pubs(db_path))
)
```

@@

@@

@@

@@

@@

@@

@@

# Researcher independence indicator (RII) part 4 - independent topics: alternative way via cosine similarity

```{r, engine="targets", RII4_2}

    # tar_target(ind_topics_cs,
    #            calc_cos_sim(topic_model, two_authors), 
    #            format = "qs")
    # 
)

@@

@@

```
# Article

@@

etc... rinse and repeat

>>>>

Here we import all the data we work with. Data are stored on a cloud from where we download it.

@@

     # tar_target(ids_path, here::here("data", "raw", "supervisors_updated.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     # tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(cep_investigators_arrow, arrow::read_feather(cep_investigators_path)),
     tar_target(cep_details_arrow, arrow::read_feather(cep_details_path)),
     tar_target(riv_details_arrow, arrow::read_feather(riv_details_path)),
     tar_target(riv_authors_arrow, arrow::read_feather(riv_authors_path)),
     tar_target(name = db_path, 
                command = transcribe_database(path = here::here("data",
                                                                "raw",
                                                                "czech_sci_db.sqlite"),
                                              authors_arrow, 
                                              cep_investigators_arrow,   
                                              cep_details_arrow, 
                                              riv_details_arrow, 
                                              riv_authors_arrow,
                                              text_arrow),
                format = "file"
                ),
     tar_target(sup_control, read.csv(sup_path)),
     tar_target(sup_control_second, read.csv(sup_path_second))

@@

# Matching

Here we perform construction of control groups via mahalanobis distance matching. There are 2 control groups: funded, and unfunded, which have separate matching procedures, but later are combined into one dataset (target "matching") so it is easier to work with.

```{r, engine="targets", matching}
list(

      tar_target(matching_data, match_data_prep(db_path, ids, gender, sup_control)),
      tar_target(matched_obj_unfunded, match_obj_unfunded(matching_data)), 
      tar_target(matched_obj_funded, match_obj_funded(db_path, matching_data)),
      tar_target(matching, match_data(matched_obj_unfunded, matched_obj_funded))

# Data preparation

Here we perform author disambiguation of the manually collected names of supervisors ("sup_complete", "ids_complete") and combine these into final dataset including list of publications for each observation (in the target "all_authors").

Further, we prepare the data for the construction of topic models in the targets "all_pubs" and "random_pubs".

```{r, engine="targets", data_prep}
list(

 tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
      tar_target(final_data, connect_data(matching, db_path, ids_complete, sup_complete)),

      tar_target(all_authors,
           read_all_authors(db_path, ids_complete, final_data)),

     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
     tar_target(random_pubs,
           get_random_pubs(db_path))

@@

Here we construct a smaller topic model based on the randomly selected 1200 publications ("topic_model_original") from the full database of all Czech publications. Then we take all publications of the researchers in our sample (both treatment group and control groups, target "topic_model_input_addition") and match it onto the existing topic model ("topic_model"). This way we limit the endogeneity of the topic model, compared to if we calculated the topic model based only on the publications of our sample researchers.

@@

Here we construct coauthorship network for each observation in our sample, which is a precursor from which 2 parts of the independence indicator are calculated.

@@

Here we calculate first part of the independence indicator: eigenvector centrality of the PhD supervisors in the author's network.

@@

Here we calculate second part of the independence indicator: clustering coefficient of the PhD supervisors in the author's network.

@@

Here we calculate third part of the independence indicator: ratio of publications without coauthorship with the author's PhD supervisor.

@@

Here we calculate fourth part of the independence indicator: ratio of topics that the author publishes on that their PhD supervisor does not publish on.

@@

@@

Here we construct the final independence indicator using the parts calculated above.

@@

# Article

Here is the paper presenting results. It also contains code for figures, hypothesis testing, etc..

@@
